Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2023-01-03 response_to_reviewers_R1.Rmd

> We have added a sentence defining what an absorbing state is: "An absorbing state is a link in a Markov chain from which there are no possible transitions (i.e., it is the end of the chain)."

- In Section 2.1.3, you make the comment “they estimate that a better strategy would
be worth about 0.4 wins per season on average, a substantial amount in a season with
only 16 games.” This makes sense, but previously in Section 2.1.2 you mentioned
a potential difference of 3.8 wins per season, yet didn’t comment on the significant
magnitude of that effect. I’m not advocating for a particular change here, but the
authors could consider adding a small comment about the size of the effect Pelechrinis
et. al. estimated.
- At the end of Section 2.1.3, you write “Lopez (2020) also concludes that coaches are
too conservative on 4th down decision making, but the effect may be overstated due
to the way in which to go yardage has been recorded in the past.” It’s unclear to me
whether the overstated effect is the one Lopez estimates in his paper, or if you are
referring to the estimated effects past studies which used less granular data.
- In Section 2.3, you write “NHL coaches do not always employ the optimal strategies”,
but it isn’t clear what those strategies are in reference to the previous discussion. Is
pulling the goalie optimal?
- In the second formula of Section 4.1, the right hand side of the equation has a 2, but
it should be an α.

> Thank you. This is fixed.

- I think Section 5.2 would benefit from a short introductory paragraph, perhaps which
introduces different types of sports betting, thus leading into the betting pools discussion of Section 5.2.1.

> Thank you for this suggestion. We have a added a short paragraph to this effect.

- I notice you have several hyperlinks throughout–I’m not sure what the Wiley standards
are, but it might be helpful to distinguish links with a different color.

### 2023-01-03 sports_analytics.Rmd
added intro paragraph on betting; #43

>>>>

Many different types of bets can be placed on sports. 
For individual contests, bets involve point spreads, moneylines, odds, or other ways of handicapping which team will win. 
Money can also be wagered on futures, where odds are given in advance for events that may or may not transpire (e.g., a certain team making the playoffs, or a certain player winning the MVP award). 
Here, we focus on betting pools, in which a group of people compete to predict winners in multiple contests (often a tournament), and the inevitable question of whether strategies exist that will consistently beat the market.
